---
title: "Additional exploration"
output: github_document
---

<!---# Source - https://stackoverflow.com/a
# Posted by Thomas
# Retrieved 2025-12-09, License - CC BY-SA 3.0 -->


First some code from the reproducible example is repeated to use the same time frame

```{r echo=FALSE}
knitr::opts_chunk$set(cache = TRUE)
invisible(knitr::purl("case_study_3_reproducable.Rmd", output="temp.R", quiet=TRUE))
knitr::read_chunk("temp.R")
```

```{r ref.label='requiredPkg'}
```
```{r ref.label='datetime'}
```

```{r echo=FALSE}
unlink("temp.R")
```
Lets take a bit wider interval to see the context


```{r interv}
small_scale_radar_interval<-lubridate::interval(time-hours(10), time+hours(10))
```
## Robin Radars located at sea

To investigate the high densities at sea we analyse two robin radars located there. 

```{r uvaRR}
require(uvaRR)
trks <- purrr::map(
  c("rws01", "borssele"),
  ~ rr_track(
    database = .x,
    ts =c(int_start(small_scale_radar_interval), int_end(small_scale_radar_interval)) ,
    interv = 60 * 60,
    geom = T,
    classification = c("BIRD"),
    movement_metrics = c("dir", "dist", "edist", "spd", "str", "z")
  ) |>
    tibble::add_column(radar = .x)
) |>
  bind_rows() |>
  mutate(trajectory = sf::st_as_sfc(trajectory, crs = 4326)) |>
  st_as_sf() |>
  mutate(
    radarid_unique = trajectory_radarid |>
      purrr::map(
        ~ unlist(purrr::map(
          purrr::map(strsplit(gsub("\\{|\\}", "", .x), ","), as.numeric),
          unique
        ))
      ),
    radarid_unique_chr = purrr::map_chr(
      purrr::map(radarid_unique, as.character),
      paste,
      collapse = " "
    ),
    radar_type = case_match(
      radarid_unique_chr,
      c("11 14", "5 8") ~ "mixed",
      c("14", "8") ~ "vertical",
      c("11", "5") ~ "horizontal"
    )
  )
```
There is an increased density of birds in Luchterduinen (`rws01`) while this is absent from Borssele.
```{r rrplot}
ggplot(trks) +
  geom_histogram(aes(x = timestamp_start, fill = classification)) +
  facet_grid(radar ~ .) +
  geom_vline(xintercept = time)
ggplot(trks) +
  geom_histogram(aes(x = timestamp_start, fill = radar_type)) +
  facet_grid(radar ~ .) +
  geom_vline(xintercept = time)
```
A directional histogram seems to confirm that the movements are vey directional corresponding to migratory movements
```{r dirhist}
ggplot(
  trks |>
    dplyr::filter(
      radar_type != "vertical",
      timestamp_start <
        lubridate::ceiling_date(time + lubridate::hours(2), "hours"),
      timestamp_start >
        lubridate::floor_date(time - lubridate::hours(2), "hours")
    )
) +
  geom_histogram(aes(x = dir, fill = radar_type), binwidth = 30) +
  facet_grid(radar ~ lubridate::floor_date(timestamp_start, "hour")) +
  coord_polar() +
  scale_x_continuous(limits = c(0, 360), breaks = 0:3*90)
```


## MR1 Radars


```{r mr1}
bs_radar_databases = c("sbrs_kid_bs291", "sbrs_ams_bs290")
bs_data <- purrr::map(
  bs_radar_databases, ~
    DBI::dbGetQuery(
      as.is = F,
      uvaAuth::get_connection_postgresql(.x),
      glue::glue(
        "select * from collection left join rf_classification on rf_classification.echo = collection.row
      left join rfclasses on rfclasses.id = rf_classification.class  where time_stamp between '{format(lubridate::int_start(small_scale_radar_interval))}' and '{format(lubridate::int_end(small_scale_radar_interval))}';
"
      )
    ) |>
      dplyr::mutate(
        speed = feature3,
        azimuth = feature2,
        altitude_AGL = feature1
      ) %>%
      dplyr::select(-starts_with("feature")) %>%
      tibble::add_column(database = .x)
) |>
  bind_rows()

```

```{r explore}
bs_data_filtered<-bs_data |> dplyr::filter(!name%in%c('insect', 'undefined', 'nonbio','precipitation'))
table(bs_data$name)

ggplot(bs_data_filtered) +
  geom_histogram(aes(x = time_stamp, fill = name)) +
  facet_grid(database ~ .) +
  geom_vline(xintercept = time)
```

Here we see that the radar in Kijkduin has a migratory peak in the morning while that is absent from Amsterdam.

Lets explore the directions in Kijkduin:
```{r dirhistBs}
ggplot(
  bs_data_filtered |>
    dplyr::filter(
     database=='sbrs_kid_bs291',
      time_stamp <
        lubridate::ceiling_date(time + lubridate::hours(2), "hours"),
      time_stamp >
        lubridate::floor_date(time - lubridate::hours(2), "hours")
    )
) +
  geom_histogram(aes(x = azimuth, fill = name), binwidth = 15) +
  facet_wrap(. ~ lubridate::floor_date(time_stamp, "hour")) +
  coord_polar() +
  scale_x_continuous(limits = c(0, 360), breaks = 0:3*90)
```
